### 2013-09-13 thesis/src/chapters/chapter-3.tex
Spellings
Added two more models

\section{Data analysis}
Having policies defined, their conditions are evaluated against data acquired from sensors. In a simplest case this evaluation can be based on a Threshold Model \cite{LiWoZh05}, which defines a valid range. In cases when given metric violates that condition (i.e. value is either smaller than minimal or bigger than maximal acceptable) corresponding resource is properly adjusted. While trivial in its form, cases of AWS, OpenShift, Carina, OneCloud proves it is useful in a real-world scenarios. Having that said, more sophisticated algorithms also exists:
\begin{itemize}
  \item \textit{integer programming} - auto scaling is reduced to server integer programming problems, which aims to minimize the cost or maximize the computing power with either computing power constraints or
budget constraints \cite{MaLiHu10}
  \item \textit{prediction error correction} - \cite{ShSuGuWi11}
  \item \textit{linearised dynamic control} - linearised correction model is based on control equations \cite{AbShBh02}:

>>>>

\section{Data analysis}
Having policies defined, their conditions are evaluated against data acquired from sensors. In a simplest case this evaluation can be based on a Threshold Model \cite{LiWoZh05}, which defines a valid range. In cases when given metric violates that condition (i.e. value is either smaller than minimal or bigger than maximal acceptable) corresponding resource is properly adjusted. While trivial in its form, cases of AWS, OpenShift, Carina, OneCloud proves it is useful in a real-world scenarios. Having that said, more sophisticated algorithms also exists:
\begin{itemize}
  \item \textit{integer programming} - auto scaling is reduced to server integer programming problems, which aims to minimize the cost or maximize the computing power with either computing power constraints or
budget constraints \cite{MaLiHu10}
  \item \textit{burst based padding} - employs a signal processing technique based on fast Fourier transform, burst pattern is extracted and used to calculate a padding value. Coefficients that represents the amplitude of each frequency component are used to calculate burst density. Depending of that value (i.e. is higher than 50\%) appropriate percentile of the burst values are used \cite{ShSuGuWi11}  
  \item \textit{remedial padding} - padding errors are being recorded and used in successive padding evaluations. In other words, let $e_1, e_2, ... e_k$ denote the recent prediction errors, next the weighted moving average is calculated. Actual applied padding is either padding itself or weighted average, depending which one is greater \cite{ShSuGuWi11}    
  \item \textit{linearised dynamic control} - linearised correction model is based on control equations \cite{AbShBh02}:
